Debugging of RxJS-Based Applications

### 2020-10-15 paper.tex
Latest ACM

\documentclass[sigplan,screen]{acmart}
% Class options:
%  - review: Show line numbers for reviewers
%  - nonacm: Hide ACM conference stuff

@@

%%% The following is specific to REBLS '20 and the paper
%%% 'Debugging RxJS-Based Applications'
%%% by Manuel Alabor.
%%%
\setcopyright{acmlicensed}
\acmPrice{15.00}
\acmDOI{10.1145/3427763.3428313}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{splashws20reblsmain-p3-p}
\acmISBN{978-1-4503-8188-8/20/11}
\acmConference[REBLS '20]{Proceedings of the 7th ACM SIGPLAN International Workshop on Reactive and Event-Based Languages and Systems}{November 16, 2020}{Virtual, USA}
\acmBooktitle{Proceedings of the 7th ACM SIGPLAN International Workshop on Reactive and Event-Based Languages and Systems (REBLS '20), November 16, 2020, Virtual, USA}

% Top Matter: https://mirror.kumi.systems/ctan/macros/latex/contrib/acmart/acmart.pdf
\title{Debugging of RxJS-based Applications}
\author{Manuel Alabor}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{manuel.alabor@ost.ch}

\author{Prof. Dr. Markus Stolze}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{markus.stolze@ost.ch}

@@

\begin{listing}
	\begin{minted}{TypeScript}
		<anonymous> RxJS
			rxjs 6.5.2/internal/operators/map.js:49
			rxjs 6.5.2/internal/Subscriber.js:66
			rxjs 6.5.2/internal/observable/interval.js:23
			rxjs 6.5.2/internal/scheduler/AsyncAction.js:71
			// ...
	\end{minted}
	\caption{A call stack showing the internal RxJS execution stack for a breakpoint in the arrow function on Line~2 in Listing~\ref{lst:rxjs-debugging}.}
	\label{lst:rxjs-call-stack}
\end{listing}

>>>>

\documentclass[sigplan,screen]{./acmart}
% Class options:
%  - review: Show line numbers for reviewers
%  - nonacm: Hide ACM conference stuff

@@

%%% The following is specific to REBLS '20 and the paper
%%% 'Debugging RxJS-Based Applications'
%%% by Manuel Alabor.
%%%
\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmlicensed}
\acmConference[REBLS '20]{Proceedings of the 7th ACM SIGPLAN International Workshop on Reactive and Event-Based Languages and Systems}{November 16, 2020}{Virtual, USA}
\acmBooktitle{Proceedings of the 7th ACM SIGPLAN International Workshop on Reactive and Event-Based Languages and Systems (REBLS '20), November 16, 2020, Virtual, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3427763.3428313}
\acmISBN{978-1-4503-8188-8/20/11}

% Top Matter: https://mirror.kumi.systems/ctan/macros/latex/contrib/acmart/acmart.pdf
\title{Debugging of RxJS-Based Applications}
\author{Manuel Alabor}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{manuel.alabor@ost.ch}

\author{Markus Stolze}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{markus.stolze@ost.ch}

@@

\begin{listing}
	\begin{minted}{TypeScript}
		<anonymous> RxJS
			rxjs 6.5.2/internal/operators/map.js:49
			rxjs 6.5.2/internal/Subscriber.js:66
			rxjs 6.5.2/internal/observable/interval.js:23
			// ...
	\end{minted}
	\caption{A call stack showing the internal RxJS execution stack for a breakpoint in the arrow function on Line~2 in Listing~\ref{lst:rxjs-debugging}.}
	\label{lst:rxjs-call-stack}
\end{listing}
